Arcturus: efficient proofs for confidential transactions

### 2020-04-07 paper/iacr.tex
Code and paper

\documentclass{article}
\usepackage[top=1.0in,bottom=1.0in,left=1.0in,right=1.0in]{geometry}
\usepackage{amsmath,amssymb,amsthm,amsfonts}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{graphicx}

\title{Triptych: logarithmic-sized linkable ring signatures with applications}
\author{Sarang Noether and Brandon Goodell \\ Monero Research Lab \\ \texttt{\{sarang,surae\}.noether@protonmail.com}}
\date{\today}

\newcommand{\G}{\mathbb{G}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\com}{\operatorname{Com}}
\newcommand{\hs}{\mathcal{H}}
\newcommand{\hp}{\mathbb{H}}

\newcommand{\A}{\mathcal{A}}

\newcommand{\sumi}{\sum_{i=0}^{n-1}}
\newcommand{\sumj}{\sum_{j=0}^{m-1}}
\newcommand{\sumk}{\sum_{k=0}^{N-1}}

@@

\begin{abstract}
Ring signatures are a common construction used to provide signer ambiguity among a non-interactive set of public keys specified at the time of signing.
Unlike early approaches where signature size is linear in the size of the signer anonymity set, current optimal solutions either require centralized trusted setups or produce signatures logarithmic in size.
However, few also provide linkability, a property used to determine whether the signer of a message has signed any previous message, possibly with restrictions on the anonymity set choice.
Here we introduce Triptych, a family of linkable ring signatures without trusted setup that is based on generalizations of zero-knowledge proofs of knowledge of commitment openings to zero.
We demonstrate applications of Triptych in signer-ambiguous transaction protocols by extending the construction to openings of parallel commitments in independent anonymity sets.
Signatures are logarithmic in the anonymity set size and, while verification complexity is linear, collections of proofs can be efficiently verified in batches.
We show that for anonymity set sizes practical for use in distributed protocols, Triptych offers competitive performance with a straightforward construction.
\end{abstract}

\section{Introduction}
First introduced in \cite{rivest} with respect to RSA groups, ring signatures permit the signing of messages using public key sets not fixed in advance, without the need of a trusted group manager.
Earlier constructions lacked such flexibility, requiring either centralized key setup or the establishment of fixed signing sets.
Later work \cite{bender} established more robust security models for unforgeability and anonymity, capturing realistic threat models where an adversary is permitted to corrupt keys, convince honest signers to include malicious anonymity set members, or obtain signatures in advance.

Since a ring signature has an anonymity set of public keys, one of which is the true signer, the detection of signing by the same key requires an additional property, linkability.
A linkable ring signature \cite{lsag} enables verifiers to determine whether the (unknown) signer of a message has signed other messages.
Such a construction was proposed for election applications, where it is necessary to ensure that votes are anonymous, but voters are permitted to vote only once on a particular issue.
The construction in \cite{lsag}, with a hash-trapdoor structure similar to that of \cite{schnorr}, is of particular interest due to potential flexibility in linking; while its linking is limited to signer-selected but unchanging signer anonymity sets, it permits linking on a per-issue basis.
Additional recent work in \cite{backes} introduces the property of linkable anonymity, using sets of signatures and establishing restrictions on key corruption.
Other related interesting properties like traceability \cite{fs,f} imply stronger capabilities, where an attempt to sign two messages with the same key permits verifiers to identify the signer.

Linkable ring signatures have seen particular applications in signer-ambiguous transaction protocols.
In such an application, transactions are authorized by a ring signature whose signing anonymity set consists of previously-generated transaction outputs.
A signature demonstrates that the signer controls the private key of one such output without revealing which is the signer, and linkability is used to assure verifiers that output has not been used in another signature (signifying a double-spend attempt).

A practical consideration for the use of linkable ring signatures in transaction protocols is how signature size and verification time scale with the size of the anonymity set.
In common applied constructions like \cite{mlsag,clsag}, signature size and verification time scale linearly with the size of the signing ambiguity set; since such signatures are typically included in a public distributed data structure like a blockchain, there is a balance between the size of the anonymity set and the requirements for storage and verification.
Recent protocol work in this area mitigates the size restriction.
For example, in \cite{rct3}, the authors introduce a confidential transaction protocol based on a proving system whose size scales logarithmically with the anonymity set size, and which includes a method for demonstrating amount balance; amount commitment range proving is offloaded to other constructions like \cite{bulletproofs}.
In \cite{omniring}, the authors use a more general proving technique to accomplish a similar goal; however, the protocol offers further size benefits by integrating commitment range proofs into the proof structure directly, taking advantage of the logarithmic proof size.

Other signer-ambiguous transaction protocols not based on linkable ring signatures offer more competitive performance.
For example, protocols like \cite{zcash} produce maximal theoretical signer ambiguity through the use of zero-knowledge Merkle proofs (among others) that offer extremely small proofs with low verification time, but at the cost of a trusted structured setup process that arises from the underlying proving system \cite{groth16}.
Like this work, \cite{lelantus} is a transaction protocol also based on \cite{groth}; however, it is intended to operate on commitments similar to those used in \cite{zerocoin} but with the inclusion of amounts, and has limitations on addressing and sender tracing.

\subsection{Our contribution}
We produce a family of linkable ring signatures, which we call Triptych.
The constructions are a linkable generalization of Groth's one-of-many commitment-to-zero proving system \cite{groth}, with optimizations from Bootle \cite{bootle} applied for improvements to proof size and verification complexity.
In the simplest version of Triptych, the prover shows that it knows the opening of a commitment to zero within a commitment set, and also that it has constructed a linking tag using the same opening, producing a linkable ring signature construction.
We then modify Groth's ring signature definitions to include linkability and a related property, non-frameability.

In an extension of Triptych, we include multiple independent sets of commitments.
Here, the prover proceeds as before to show its knowledge of an opening to a commitment in one set, as well as the construction of the linking tag.
However, the proof also shows that the prover knows an opening of a commitment at the same position in all other sets.
This construction has immediate application; in some signer-ambiguous confidential transaction protocols, transaction inputs are commitments to zero, for which the signer shows it knows the opening.
Each commitment comes equipped with another commitment to the amount of the input; by offsetting these commitments homomorphically and carefully choosing commitment randomness, the prover can show that a particular transaction balances.

We show that Triptych produces signatures with competitive performance to other modern linkable ring signatures for limited anonymity set sizes.
We note that similar constructions also require linear verification time, meaning that the size of anonymity set used in practice is likely to be limited for performance reasons.

\section{Preliminaries}
\subsection{Public parameters}
Let $\G$ be a cyclic group in which the discrete logarithm problem is hard, and let $\F$ be the scalar field of $\G$.
Let $\hs: \{0,1\}^* \to \F$ be a cryptographic hash function.
Let $G$ and $H$ be generators of $\G$ with unknown discrete logarithm relationship.
Let $N = n^m$ be a size parameter, where $n > 1$ and $m > 1$.
Let $\{G_{j,i}\}_{j,i=0}^{m-1,n-1}$ be a set of generators of $\G$ with unknown discrete logarithm relationship to each other, to $G$, and to $H$.
Let $U$ be a generator of $\G$.
Note that all generators may be produced using public randomness; for example, the use of a suitable hash function with domain separation may be appropriate.
All such public parameters are assumed to comprise a global reference string known to all players; in particular, we exclude them from algorithm definitions and Fiat-Shamir transcript hashes for readability.

\subsection{Pedersen commitment}
Let $\com$ be a homomorphic commitment scheme that is perfectly hiding and computationally binding.
In this work, we assume use of the Pedersen commitment scheme: for $x,r \in \F$, define $\com(x,r) \equiv xG + rH$ to be the commitment of the value $x$ with randomness $r$.
This can be trivially extended to support matrix values; for $\{x_{j,i}\},r \in \F$, define $\com(x,r) \equiv rH + \sum_{j,i} x_{j,i}G_{j,i}$.
Note in particular that Pedersen matrix commitments are similarly homomorphic.

@@

We sometimes use index subscript notation of the form $i_j$ to indicate the $j$ digit of $i$, where such a decomposition of $i$ is taken base $n$ with padded length $m$:
$$\sum_{j=0}^m i_j n^j = i$$
This notation will be specified explicitly where confusion may occur.

\section{Protocol: linkable one-of-many commitment}
We wish to build a linkable ring signature construction, where a signer who knows the opening of a commitment may sign messages using an anonymity set containing other commitments for which the signer does not know openings.
Included with the proof of knowledge, the signer also provides a linking tag that is the image of the signing commitment's opening under a verifiable pseudorandom function, using the method of \cite{dodis} that has previously appeared in \cite{omniring,rct3}.
Part of the soundness of the proving system relies on the proper construction of this linking tag.
Upon receipt, a verifier can check whether the linking tag has previously appeared in any other valid proof; if it has not, injectivity assures the verifier that no other signature has been produced by the (unknown) signer.

More specifically, we modify the construction of Bootle \cite{bootle}, which itself is a generalization of a construction by Groth \cite{groth}.
We produce a sigma protocol for the following relation:
$$\mathcal{R}_{\text{link}} = \left\{ \{M_i\}_{i=0}^{N-1} \subset \G, J \in \G ; (l \in \mathbb{Z},r \in \F) : M_l = rG \text{ and } U = rJ \right\}$$
Figures \ref{fig:link} and \ref{fig:link_2} describe the protocol.

\begin{figure}[htbp]
\centering
\fbox{\begin{minipage}{0.95\textwidth}
$\underline{\mathcal{P}_{\text{link}}(\{M_i\},J;(l,r)):}$
\begin{itemize}
\item Select random $r_A \in \F$ and $\left\{a_{j,i}\right\}_{i=1,j=0}^{n-1,m-1} \subset \F$.
Define $A \equiv \com(a,r_A)$.
\item Define $\left\{\sigma_{j,i}\right\}_{i,j=0}^{n-1,j-1} \subset \F$ such that $\sigma_{j,i} \equiv \delta\left(l_j,i\right)$ (using our decomposition notation), and choose random $r_B \in \F$.
Define $B \equiv \com(\sigma,r_B)$.
\item Select random $r_C \in \F$, and define $C \equiv \com(a(1-2\sigma), r_C)$.
\item Select random $r_D \in \F$, and define $D \equiv \com(-a^2, r_D)$.
\item Define coefficients $\left\{p_{k,j}\right\}_{k,j=0}^{N-1,m-1}$ such that $$p_k(x) \equiv \prod_{j=0}^{m-1} \left( \sigma_{j,k}x + a_{j,k} \right) = \delta\left(l,k\right)x^m + \sumj p_{k,j}x^j$$ for all $k \in [0,N)$ (using our decomposition notation).
\item Select random $\left\{\rho_j\right\}_{j=0}^{m-1} \subset \F$.
\item Define $\{X_j\}_{j=0}^{m-1} \subset \G$ such that: $$X_j \equiv \sumk p_{k,j}M_k + \rho_jG$$
\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv U \sumk p_{k,j}+ \rho_jJ$$
\end{itemize}

$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
$A,B,C,D,\{X_j\},\{Y_j\}$ \\

$\underline{\mathcal{V} \to \mathcal{P}:}$ \\
$\xi \in \{0,1\}^*$ \\

$\underline{\mathcal{P}(\xi):}$
\begin{itemize}
\item Define $\left\{f_{j,i}\right\}_{i=1,j}^{n-1,m-1}$ such that $f_{j,i} \equiv \sigma_{j,i}\xi + a_{j,i}$.
\item Define $z_A \equiv r_A + \xi r_B$ and $z_C \equiv \xi r_C + r_D$.
\item Define $z \equiv r \xi^m - \sumj \rho_j \xi^j$.
\end{itemize}

$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
$\{f_{j,i}\}_{j=0,i=1}^{m-1,n-1},z_A,z_C,z$
\end{minipage}}
\caption{Sigma protocol for $\mathcal{R}_{\text{link}}$}
\label{fig:link}
\end{figure}

\begin{figure}[htbp]
\centering
\fbox{\begin{minipage}{0.95\textwidth}
$\underline{\mathcal{V}_{\text{link}}(\{M_i\},J):}$
\begin{itemize}
\item For $0 \leq j < m$, let $f_{j,0} \equiv \xi - \sum_{i=1}^{n-1} f_{j,i}$.
\item Accept if and only if:
\begin{eqnarray}
A + \xi B &=& \com(f,z_A) \label{eqn:ab} \\
\xi C + D &=& \com(f(\xi-f),z_C) \label{eqn:cd} \\
\sumk M_k \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jX_j - zG &=& 0 \label{eqn:x} \\
U \sumk \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jY_j - zJ &=& 0 \label{eqn:y}
\end{eqnarray}
\end{itemize}
\end{minipage}}
\caption{Sigma protocol for $\mathcal{R}_{\text{link}}$ (continued)}
\label{fig:link_2}
\end{figure}

Observe that this protocol can be made non-interactive using the Fiat-Shamir heuristic, where the verifier challenge is produced using a collision-resistant hash function (modeling a random oracle) and the proof transcript \cite{fiatshamir}.

We will show that the sigma protocol is complete, sound, and zero-knowledge, the precise definitions of which are common and found in \cite{groth}.
Informally, we require the protocol be:
\begin{itemize}
\item \textit{Perfectly complete}: Given knowledge of a witness to a statement in the proof relation, an honest prover can always convince an honest verifier of the validity of the witness.
\item \textit{Special sound}: Given a statement in the proof relation, if a prover can answer multiple verifier challenges correctly, then it is possible to extract a witness for this statement.
\item \textit{Special honest-verifier zero knowledge}: Given any statement and verifier challenge, it is possible to simulate a transcript that is accepted by an honest verifier without knowledge of a corresponding witness.
\end{itemize}

\begin{theorem}
The protocol in Figures \ref{fig:link} and \ref{fig:link_2} is perfectly complete, special honest-verifier zero knowledge, and $(m+1)$-special sound.
\end{theorem}

\begin{proof}
The proof follows similarly to that of \cite{bootle}.

% Completeness
We first show perfect completeness.
Suppose the verifier receives a proof generated by an honest prover.
Equation \ref{eqn:ab} holds using the identity $$\sumi \sigma_{j,i} = 1$$ for all $0 \leq j < m$.
Equation \ref{eqn:cd} follows similarly, using the identity $$\left(\sigma_{j,i}\right)^2 = \sigma_{j,i}$$ for all $0 \leq j < m$.
To show Equation \ref{eqn:x} holds:
\begin{eqnarray*}
&& \sumk M_k \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jX_j - zG \\
&=& \sumk M_k p_k(\xi) - \sumj \xi^j \left( \sumk p_{k,j}M_k + \rho_jG \right) - zG \\
&=& \sumk M_k \left( p_k(\xi) - \sumj \xi^j p_{k,j} \right) - \sumj \xi^j \rho_jG - zG \\
&=& \sumk M_k \xi^m \delta(l,k) - \sumj \xi^j \rho_jG - \left( r\xi^m - \sumj \rho_j\xi^j \right)G \\
&=& \xi^mrG - \sumj \xi^j \rho_jG - \xi^mrG + \sumj \xi^j \rho_jG \\
&=& 0
\end{eqnarray*}
Equation \ref{eqn:y} follows similarly:
\begin{eqnarray*}
&& U \sumk \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jY_j - zJ \\
&=& U \sumk p_k(\xi) - \sumj \xi^j \left( U \sumk p_{k,j} + \rho_jJ \right) - zJ \\
&=& U \sumk \left( p_k(\xi) - \sumj \xi^j p_{k,j} \right) - \sumj \xi^j \rho_jJ - zJ \\
&=& U \sumk \xi^m \delta(l,k) - \sumj \xi^j \rho_jJ - \left( r\xi^m - \sumj \rho_j\xi^j \right)J \\
&=& \xi^mU - \sumj \xi^j \rho_jG - \xi^mrJ + \sumj \xi^j \rho_jG \\
&=& 0
\end{eqnarray*}
since $J = r^{-1}U$ in a valid proof.
Hence the protocol is perfectly complete.

% SHVZK
We next show that the protocol is special honest-verifier zero knowledge.
To do so, we construct a simulator that, given a random verifier challenge $\xi$, can construct a proof transcript with identical distribution to a valid proof.

First, observe that the simulator presented in the proof of Lemma 1 in \cite{bootle} translates identically to our setting.
If the simulator chooses $B \in \G$ uniformly at random, the cited lemma assures us a valid simulation of the proof elements $A,C,D,z_A,z_C,\{f^{(u)}_{j,i \neq 0}\}$; we may compute each $f^{(u)}_{j,0}$ from this.
Further, in a valid proof, $B$ is independent and uniformly distributed as well.

The proof elements $\{X_j\}_{j=1}^{m-1}$ and $\{Y_j\}_{j=1}^{m-1}$ are independent and uniformly distributed in a valid proof since the set $\{\rho_j\}$ is random and the discrete logarithm problem in $\G$ is hard, so the simulator may choose these uniformly at random.
The verification checks require that $X_0$ and $Y_0$ be uniquely determined by the other elements in the corresponding sets in both real proofs and by the simulator.

>>>>

\documentclass{article}
\usepackage[top=1.0in,bottom=1.0in,left=1.0in,right=1.0in]{geometry}
\usepackage{amsmath,amssymb,amsthm,amsfonts}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{graphics,graphicx}

\title{Arcturus: efficient proofs for confidential transactions}
\author{Sarang Noether \\ Monero Research Lab \\ \texttt{sarang.noether@protonmail.com}}
\date{\today}

\newcommand{\G}{\mathbb{G}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\hs}{\mathsf{H}}
\newcommand{\hp}{\mathcal{H}}
\newcommand{\com}{\operatorname{Com}}
\newcommand{\A}{\mathcal{A}}

\newcommand{\sumi}{\sum_{i=0}^{n-1}}
\newcommand{\sumj}{\sum_{j=0}^{m-1}}
\newcommand{\sumk}{\sum_{k=0}^{N-1}}
\newcommand{\sumu}{\sum_{u=0}^{w-1}}

@@

\begin{abstract}
Confidential transactions are used in distributed digital assets to demonstrate the balance of values hidden in commitments, while retaining signer ambiguity.
Previous work describes a signer-ambiguous proof of knowledge of the opening of commitments to zero at the same index across multiple public commitment sets and the evaluation of a verifiable random function used as a linking tag, and uses this to build a linkable ring signature called Triptych that can be used as a building block for a confidential transaction model.
In this work, we extend Triptych to build Arcturus, a proving system that proves knowledge of openings of multiple commitments to zero within a single set, correct construction of a verifiable random function evaluated at each opening, and value balance across a separate list of commitments within a single proof.
While soundness depends on a novel dual discrete-logarithm hardness assumption, we use data from the Monero blockchain to show that Arcturus can be used in a confidential transaction model to provide faster total batch verification time than other state-of-the-art constructions without a trusted setup.
\end{abstract}

\section{Introduction}
Distributed digital assets, starting with Bitcoin, rely on digital signatures to authorize transactions and transfer the spend authority of funds.
While early protocols based on the model established by Bitcoin have the advantage of simplicity, they lack desirable properties relating to privacy and indistinguishability.
In particular, the address and signature graph formed by the blockchain in such assets is trivially traceable, and the amounts a signature authorizes in a transaction are visible.

To protect users of distributed assets and permit better indistinguishability of transactions for fungibility, several methods have been proposed and deployed toward confidential transactions.
The CryptoNote protocol, an early proposal for obscuring transaction graphs, relies on linkable ring signatures on transaction outputs with denominated amounts \cite{cryptonote}; a transaction includes a separate signature for each such amount, yielding poor scaling.
A later advancement to the RingCT protocol \cite{ringct} used Pedersen commitments to amounts associated with transaction outputs and extended a ring signature construction by Liu \text{et al.} \cite{liu} to support parallel signatures in a matrix arrangement, removing the need for denominated transaction outputs altogether.
However, both of these constructions use linkable ring signatures that scale linearly in size with the size of the anonymity set used in each signature.

More recent methods of maintaining transaction privacy use accumulators to represent a given state of transaction outputs.
Zerocoin \cite{zerocoin} relied on RSA accumulators and associated proofs to assert the validity of transactions, but amounts were fixed, the protocol used very large and inefficient proofs, transactions were limited to a simple burn-mint operation on a transparent chain, and the use of RSA groups required a trusted setup process.
Later work produced Zerocash \cite{zerocash}, which replaced RSA accumulators and related proofs with succinct proofs relating to Merkle tree accumulators, enabling arbitrary amounts and direct anonymous transfers.
However, like Zerocoin, Zerocash used a proving system requiring a trusted setup process; this was eventually used as the basis for the Zcash protocols.

Until recently, transaction protocols desiring robust signer ambiguity and flexible direct anonymous transfers of arbitrary amounts faced a tradeoff between a trust-free construction and efficiency in proof sizes and verification complexity.
Recent work in this area generally relies on one of two novel proving systems to build transactions that scale in size logarithmically with the size of the prover-specified anonymity set, while requiring no trusted setup.
A one-of-many commitment-to-zero proving system of Groth and Kohlweiss \cite{groth} was used to build simple ring signatures and Zerocoin-style transactions, and was later extended to support accountable ring signatures more efficiently by Bootle \cite{bootle}.
This proving system forms the basis of Lelantus \cite{lelantus}, which extends the Zerocoin-style transaction model of \cite{groth} by using multiple-base Pedersen commitments to incorporate amounts alongside serial numbers; a modification to the proofs shows balance, and multiple proofs are needed for typical transactions.
However, Lelantus transactions allow a transaction sender to later identify when the recipient spends their funds; a mitigation to this solves the tracing problem, but at the cost of eliminating a useful one-time addressing construction that ensures recipient anonymity.
The same proving system in \cite{groth} is used in Triptych \cite{triptych}, a multi-dimensional linkable ring signature construction that can be used to build confidential transactions similarly to \cite{ringct}; Triptych notably supports one-time addressing and arbitrary amounts, while still requiring the use of multiple proofs for transactions spending multiple transaction outputs.
Interestingly, recent independent work extends \cite{groth} to support proofs on multiple commitments in a single list (as we also introduce below), with a particular application to Zether \cite{zether}; however, this uses a different approach than we take here, and seems to result in larger proofs.

The Bulletproofs \cite{bulletproofs} proving system uses an inner-product compression method to build range and circuit satisfiability proofs with logarithmic size scaling.
Besides an increasingly widespread deployment for commitment range proofs, the underlying structure of Bulletproofs is used to construct more specialized proving systems for confidential transactions.
Omniring \cite{omniring} uses this method to build transactions that demonstrate spend authorization for multiple signer-ambiguous transaction inputs within a single proof, while directly integrating range proving.
The result is very small proofs; however, verification is slower than other approaches, and requirements for unique group generators mean such proofs cannot be verified in efficient batches.
RingCT 3.0 \cite{rct3} also uses a Bulletproof-style construction.
In an early version, transactions required separate proofs for multiple inputs; while an update incorporates a single proof for all inputs to a transaction, it also requires that the number of inputs be padded to a power of two, which can yield poor verification complexity.

\subsection{Our contribution}
We extend the proving system in Triptych \cite{triptych} in two significant ways, which we call Arcturus.
First, we enable the prover to show knowledge of multiple signing keys in a single proof simultaneously using one set of combined proof elements; unlike \cite{rct3}, our modification admits any number of transaction inputs without limitations.
We retain the verifiable random function evaluation that produces linking tags, which are required for the detection of repeat signing with the same commitment opening across proofs.
Second, we show Pedersen commitment value balance directly within the same proof; in particular, we show that a particular combination of input and output commitments sums to a commitment to zero.
We note that the soundness of the resulting proving system depends on a novel dual discrete-logarithm hardness assumption that we are not able to reduce to a standard hardness assumption; while we consider this novel assumption reasonable, it is untested.

Taken together, these changes have application to a transaction protocol for efficient use in blockchain confidential transactions that does not require any trusted setup process.
A transaction can sign for multiple signer-ambiguous inputs and prove that the transaction balances using a single proof, a major improvement to currently-deployed constructions that require multiple proofs and separate auxiliary Pedersen amount commitments.
Further, we use actual blockchain data from the Monero digital asset project to directly compare the overall size and verification time of Arcturus to that of Triptych and two separate RingCT 3.0 constructions.
We find that Arcturus provides superior verification performance compared to other trust-free confidential transaction constructions, with competitive size scaling.

\section{Preliminaries}
\subsection{Public parameters}
Let $\G$ be a cyclic group in which the discrete logarithm problem is hard, and let $\F$ be its scalar field.
Let $\hs: \{0,1\}^* \to \F$ and $\hp: \{0,1\}^* \to \G$ be cryptographic hash functions.
Let $N = n^m$ be a positive integer, where $m > 1$ (for our construction, we will use $n = 2$).
Assume that $G$, $H$, $U$, and any point of the form $G_i$ or $H_i$ (possibly with multiple indices) are uniformly random generators of $\G$ whose discrete logarithm relationship to each other is unknown.
Note that all such generators may be produced using public randomness; for example, the use of a suitable hash function with domain separation may be appropriate.
All such public parameters are assumed to comprise a global reference string known to all players; in particular, we generally exclude explicit reference to public parameters from algorithm definitions and Fiat-Shamir transcript hashes for readability.

\subsection{Tensor commitment}
Let $\com$ be an additively homomorphic commitment scheme that is perfectly hiding and (at least) computationally binding.
In this work, we assume use of a simple extension to the Pedersen commitment scheme: for $x,r \in \F$, define $\com(x,r) \equiv rG + xH$ to be the commitment of the value $x$ with randomness $r$.

For a three-dimensional tensor $f \equiv (f_{i,j,k}) \subset \F$ and blinding factor $r \in \F$, define the Pedersen tensor commitment
$$\com(f,r) \equiv rG + \sum_{i,j,k} f_{i,j,k} G_{i,j,k}$$
using fixed independent generators as described above.

Operations on tensors are assumed to be performed componentwise; for example, if $f \equiv (f_{i,j,k})$ and $g \equiv (g_{i,j,k})$ are such tensors over $\F$, then $f + g \equiv (f_{i,j,k} + g_{i,j,k})$, and so forth.

@@

We sometimes use index subscript notation of the form $i_j$ to indicate the $j$ digit of $i$, where such a decomposition of $i$ is taken base $n$ with padded length $m$:
$$\sum_{j=0}^{m-1} i_j n^j = i$$
This notation will be specified explicitly where confusion may occur.

\subsection{Sigma protocols}
For a given relation $\mathcal{R}$, a sigma protocol for $\mathcal{R}$ is an interactive challenge-response protocol between a prover and verifier, where the prover wishes to convince the verifier it knows a witness corresponding to a statement in $\mathcal{R}$.

A sigma protocol is complete, sound, and zero-knowledge.
These definitions are well known and found, for example, in \cite{groth}.
Essentially, these properties are:
\begin{itemize}
\item \textit{Perfectly complete}: For a witness to a statement in $\mathcal{R}$, an honest prover always convinces an honest verifier of the validity.
\item \textit{Special sound}: Given a statement in $\mathcal{R}$, if the prover can produce valid proof transcripts in response to multiple verifier challenges, then it is possible to extract a witness for the statement from the transcripts.
\item \textit{Special honest-verifier zero knowledge}: Given a statement and known verifier challenge, it is possible to produce a simulated transcript without knowledge of a corresponding valid witness.
\end{itemize}
Sigma protocols can be made non-interactive by replacing random verifier challenges with hash-based transcript challenges under the random oracle model; this approach is called the Fiat-Shamir heuristic \cite{fiat}.

\subsection{Hardness assumption}
We now define a novel cryptographic hardness assumption that is used later to show the soundness of our construction.

\begin{definition}[Dual-target discrete logarithm problem]
\label{def:dual}
Let $\G$ be a group in which the discrete logarithm problem is hard, and let $\F$ be its scalar field.
Let $n > 0$.
Consider the following game between a challenger and a probabilistic polynomial-time player $\A$:
\begin{itemize}
\item The challenger chooses $G,H \in \G$ uniformly at random and sends both to $\A$.
\item $\A$ chooses and returns sets $\{G_i\}_{i=0}^{n-1},\{H_i\}_{i=0}^{n-1} \subset \G$ to the challenger.
\item The challenger chooses a set $\{\mu_i\}_{i=0}^{n-1} \subset \F$ uniformly at random and sends it to $\A$.
\item $\A$ chooses and returns a set $\{x_i\}_{i=0}^{n-1} \subset \F$ to the challenger.
\end{itemize}
We say that $\A$ wins the $(n,\epsilon,t)$-dual-target discrete logarithm game if, in time less than $t$ and with probability at least $\epsilon$, the following are true:
\begin{itemize}
\item $\sumi \mu_i \left( G_i - x_iG \right) = 0$
\item $\sumi \mu_i \left( H - x_iH_i \right) = 0$
\item There exists an index $0 \leq i < n$ such that either $x_iG \neq G_i$ or $x_iH_i \neq H$.
\end{itemize}
\end{definition}

\section{Proving system}
We now present a sigma protocol for the following relation:
\begin{multline*}
\mathcal{R} \equiv \Bigg\{ \{M_i\}_{i=0}^{N-1},\{P_i\}_{i=0}^{N-1},\{J^{(u)}\}_{u=0}^{w-1},\{Q_j\}_{j=0}^{T-1} \subset \G \: ; \: \left( \{l^{(u)}\}_{u=0}^{w-1}, \{r^{(u)}\}_{u=0}^{w-1}, y \right) : \\
M_{l^{(u)}} = r^{(u)}G \; \forall \: u \in [0,w) \text{ and } r^{(u)}J^{(u)} = U \; \forall \: u \in [0,w) \text{ and } \sum_{u=0}^{w-1} P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j = yG \Bigg\}
\end{multline*}
This captures the necessary elements for transaction authorization, which we describe later; knowledge of signing keys $\{r^{(u)}\}$ will show that the prover has signing authority for inputs to a transaction, and knowledge of the secret key $y$ to an amount commitment difference will show that the transaction amounts balance.
Finally, comparison of the verifiable random function used to produce $\{J^{(u)}\}$ will be used to prevent attempts to sign for the same secret key without revealing the corresponding public key, which is important for signer ambiguity and double-spend protection within or between proofs.

Figures \ref{fig:sigma} and \ref{fig:sigma2} describe the prover and verifier interaction.
Next, we prove that the prover and verifer routines constitute a sigma protocol that is perfectly correct, special sound, and special honest-verifier zero knowledge.

\begin{figure}[htbp]
\centering
\fbox{\begin{minipage}{0.95\textwidth}
$\underline{\mathcal{P}:}$
\begin{itemize}
\item Select random $r_A \in \F$ and $\left\{a_{j,i}^{(u)}\right\}_{i=1,j,u=0}^{n-1,m-1,w-1} \subset \F$.
Set $$\{a_{j,0}^{(u)}\}_{j,u=0}^{m-1,w-1} \equiv -\sum_{i=1}^{n-1} a_{j,0}^{(u)}$$ and define $A \equiv \com(a,r_A)$.
\item Define $\left\{\sigma_{j,i}^{(u)}\right\}_{i,j,u=0}^{n-1,m-1,w-1} \subset \F$ such that $\sigma_{j,i}^{(u)} \equiv \delta\left(l_j^{(u)},i\right)$ (using our decomposition notation), and choose random $r_B \in \F$.
Define $B \equiv \com(\sigma,r_B)$.
\item Select random $r_C \in \F$, and define $C \equiv \com(a(1-2\sigma), r_C)$.
\item Select random $r_D \in \F$, and define $D \equiv \com(-a^2, r_D)$.
\item For $0 \leq u < w$, define coefficients $\left\{p_{k,j}^{(u)}\right\}_{k,j=0}^{N-1,m-1}$ such that $$p_k^{(u)}(x) \equiv \prod_{j=0}^{m-1} \left( \sigma_{j,k}^{(u)}x + a_{j,k}^{(u)} \right) = \delta\left(l^{(u)},k\right)x^m + \sumj p_{k,j}^{(u)}x^j$$ (using our decomposition notation).
Then define $p_{k,j} \equiv \sumu p_{k,j}^{(u)}$ and $p_k(x) \equiv \sumu p_k^{(u)}(x)$ accordingly.
\item Select random $\left\{\rho_j\right\}_{j,u=0}^{m-1,w-1}, \left\{\overline{\rho}_j^{(u)}\right\}_{j,u=0}^{m-1,w-1} \subset \F$.
\item Define aggregation coefficients $\{\mu_k\}_{k=0}^{N-1}$ using a $k$-indexed $\hs$ operation, containing all Fiat-Shamir transcript public parameters and proof elements.
\item Define $\{X_j\}_{j=0}^{m-1} \subset \G$ such that: $$X_j \equiv \sumk p_{k,j}\mu_kM_k + \sumu \rho_j^{(u)}G$$
\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv U \sumk p_{k,j}\mu_k + \sumu \rho_j^{(u)}J^{(u)}$$
\item Define $\{Z_j\}_{j=0}^{m-1} \subset \G$ such that: $$Z_j \equiv \sumk p_{k,j}P_k + \sumu \overline{\rho}_j^{(u)}G$$
\end{itemize}

$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
$A,B,C,D,\{X_j\},\{Y_j\},\{Z_j\}$
\end{minipage}}
\caption{Sigma protocol for $\mathcal{R}$}
\label{fig:sigma}
\end{figure}

\begin{figure}[htbp]
\centering
\fbox{\begin{minipage}{0.95\textwidth}
$\underline{\mathcal{V} \to \mathcal{P}:}$ \\
$\xi \in \{0,1\}^*$ \\

$\underline{\mathcal{P}(\xi):}$
\begin{itemize}
\item Define $\left\{f_{j,i}^{(u)}\right\}_{i=1,j,u=0}^{n-1,m-1,w-1}$ such that $f_{j,i}^{(u)} \equiv \sigma_{j,i}^{(u)}\xi + a_{j,i}^{(u)}$.
\item Define $z_A \equiv r_A + \xi r_B$ and $z_C \equiv \xi r_C + r_D$.
\item Define $\left\{z_R^{(u)}\right\}_{u=0}^{w-1} \subset \F$ such that: $$z_R^{(u)} \equiv \mu_{l^{(u)}}r^{(u)}\xi^m - \sumj \rho_j^{(u)}\xi^j$$
\item Define: $$z_S \equiv \xi^m \left( \sumu s^{(u)} - \sum_{j=0}^{T-1} t_j \right) - \sumj \left( \xi^j \sumu \overline{\rho}_j^{(u)} \right)$$
\end{itemize}

$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
$\{f_{j,i}^{(u)}\}_{j=0,i=1,u=0}^{m-1,n-1,w-1},z_A,z_C,\{z_R^{(u)}\},z_S$ \\
